Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-05-19 tex/scam/supplement.tex
a
minor fixes

We choose $\epsilon = \left( \frac{(sB)^2 (s
    K^{**} (sBc_u)^{1/2})}{n} \right)^{2/5}$. This choice of $\epsilon$ is a bit suboptimal but it is convenient and it is sufficient for our results. It is easy to verify that
if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
$\epsilon \in (0, sB \epsilon_3c_u]$ for some absolute constant $\epsilon_3$ as required by the bracketing number statement (Corollary~\ref{cor:convexadditive_lp}). Furthermore, conditions~\eqref{cond:simplify_covering_number} also hold.

@@

Using the same bracketing analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c B^2 \sigma \sqrt{ \frac{c_u^{1/2}}{n^{4/5}} \log \frac{nC}{\delta} }+ \lambda_n B.
\end{align*}
The condition $n \geq c_1 s\sqrt{sB}$ in the proof of Theorem~\ref{thm:convex_consistent} is satisfied here because we assume that $n^{4/5} \geq c_1 B^4 \tilde{\sigma}^2 s^5 \log^2 np$ in the statement of the theorem.
Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  c B^2 \sigma \sqrt{ \frac{1}{n} \log \frac{Cn}{\delta} }+ \lambda_n B +
  c B^3 \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{C}{\delta}}+ \lambda_n B
\end{align*}

Finally, plugging in $\lambda_n \leq 768 s \tilde{\sigma} \sqrt{
  \frac{1}{n} \log^2 np}$, we obtain
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{C}{\delta}}+ 
    c s B \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}\\
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^2 c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
\end{align*}
with probability at least $1-\delta$.

@@

Plugging this into equation~\eqref{eqn:hpsi_bound} above, we have that:
\begin{align*}
& \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
 & \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
\E \psi_U(X)^2 - \E \psi_L(X)^2 + 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }.
\end{align*}
Using our bound on the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$, we have
\begin{align*}
-4sB\epsilon - 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
4sB\epsilon + 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

We choose $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBc_u)^{1/2}}{n} \right)^{2/5}$. This choice of $\epsilon$ is a bit suboptimal but it is convenient and it is sufficient for our result.

@@

\begin{lemma}
\label{lem:additive_uniqueness}
Let $p(\mathbf{x})$ be a positive density over $[0,1]^p$. Let $f(\mathbf{x}) = \sum_{j=1}^p f_j(x_j)$ and $h(\mathbf{x}) = \sum_{j=1}^d h_j(x_j)$ be two additive functions such that $\E( f(X) - h(X) )^2 = 0$. Suppose also that $\E f_j(X_j) = 0, \E h_j(X_j) = 0$ for all $j$. Then, it must be that $\E( f_j(X_j) - h_j(X_j))^2 = 0$ for all $j$.
\end{lemma}

@@

Let $P$ be the probability measure induced by the density $p(\mathbf{x})$, so that $P(A) = \int_A p(\mathbf{x}) d\lambda$ where $\lambda$ is the Lebesgue measure. Since $p > 0$, $\lambda(A) > 0$ implies that $P(A) > 0$ as well. \\

>>>>

We choose $\epsilon = \left( \frac{(sB)^2 (s
    K^{**} (sBc_u)^{1/2})}{n} \right)^{2/5}$. This choice of $\epsilon$ is not optimal but it is convenient and it is sufficient for our results. It is easy to verify that
if $n \geq c_1 s \sqrt{sB}$ for some absolute constant $c_1$, then 
$\epsilon \in (0, sB \epsilon_3c_u]$ for some absolute constant $\epsilon_3$ as required by the bracketing number statement (Corollary~\ref{cor:convexadditive_lp}). Furthermore, conditions~\eqref{cond:simplify_covering_number} also hold.

@@

Using the same bracketing analysis as in Step 2 of the proof of Theorem~\ref{thm:convex_consistent} but setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c B^2 \sigma \sqrt{ \frac{c_u^{1/2}}{n^{4/5}} \log \frac{nC}{\delta} }+ \lambda_n B.
\end{align*}
The condition $n \geq c_1 s\sqrt{sB}$ in the proof of Theorem~\ref{thm:convex_consistent} is satisfied here because we assume that $n^{4/5} \geq c_1 B^4 \tilde{\sigma}^2 s^5 \log^2 np$ in the statement of the theorem.
Using the uniform convergence result of Lemma~\ref{lem:uniform_convergence}, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  c B^2 \sigma \sqrt{ \frac{c_u^{1/2}}{n^{4/5}} \log \frac{Cn}{\delta} }+ \lambda_n B +
  c B^3 \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{nC}{\delta}}+ \lambda_n B
\end{align*}

Finally, plugging in $\lambda_n \leq 768 s \tilde{\sigma} \sqrt{
  \frac{1}{n} \log^2 np}$, we obtain
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c B^2 \tilde{\sigma} \sqrt{\frac{c_u^{1/2}}{n^{4/5}} \log \frac{nC}{\delta}}+ 
    c s B \tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}\\
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c B^2 \tilde{\sigma} \sqrt{\frac{s^2 c_u^{1/2}}{n^{4/5}} \log^2 \frac{Cnp}{\delta}}
\end{align*}
with probability at least $1-\delta$.

@@

Plugging this into equation~\eqref{eqn:hpsi_bound} above, we have that:
\begin{align*}
& \E \psi_L(X)^2 - \E \psi_U(X)^2 - 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } \\
 & \leq 
 \| h \|_n^2 - \| h \|_P^2 \leq
\E \psi_U(X)^2 - \E \psi_L(X)^2 + 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }.
\end{align*}
Using our bound on the $L_1(P)$ norm of $\psi_U^2 - \psi_L^2$, we have
\begin{align*}
-4sB\epsilon - 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} } &\leq 
 \| h \|_n^2 - \| h \|_P^2 \\
& \leq 4sB\epsilon + 
(2sB)^2 \sqrt{ \frac{ sK^{**} (sBc_u)^{1/2} \log \frac{2}{\delta}}{ \epsilon^{1/2} n} }
\end{align*}

We choose $\epsilon = \left( \frac{ (sB)^2 sK^{**} (sBc_u)^{1/2}}{n} \right)^{2/5}$. This choice of $\epsilon$ is not optimal but it is convenient and it is sufficient for our result.

@@

\begin{lemma}
\label{lem:additive_uniqueness}
Let $p(\mathbf{x})$ be a positive density over $[0,1]^p$. Let $f(\mathbf{x}) = \sum_{j=1}^p f_j(x_j)$ and $h(\mathbf{x}) = \sum_{j=1}^p h_j(x_j)$ be two additive functions such that $\E( f(X) - h(X) )^2 = 0$. Suppose also that $\E f_j(X_j) = 0, \E h_j(X_j) = 0$ for all $j$. Then, it must be that $\E( f_j(X_j) - h_j(X_j))^2 = 0$ for all $j$.
\end{lemma}

@@

Let $P$ be the probability measure induced by the density $p(\mathbf{x})$, so that $P(A) = \int_A p(\mathbf{x}) d\lambda$ where $\lambda$ is the Lebesgue measure. Since $p(\mathbf{x}) > 0$, $\lambda(A) > 0$ implies that $P(A) > 0$ as well. \\
